### 2019-03-18 message-from-committee.tex
message-from-committee.tex: Eventually consistent formatting
message-from-committee.tex: Lose the page numbers
We'll be adding them from main-matter---the only place that matters---instead.
message-from-committee.tex: Import from mftpc-2019 tag

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{times}
\usepackage{ulem}
\setlength\parindent{0pt}
\setlength\parskip{12pt}

@@

{\sffamily
\begin{tabular}{ll}
\multirow{3}{*}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 2015}} \\ &\\
& \LARGE{Message from the Organizing Committee} \\
&\\
\hline
\end{tabular}}
\vspace{2em}

{\large \bf \sffamily Heading}

Welcome, my dear friends, to the {\em very tentth} annual
Intercalary Symposium about Workshop on Robot Dance Conference in Party of Harry Q. Bovik's $10^{1.80617997398}$th Birthday!
This edition of the Party is a very special one, as the edition number coincides with the common human counting base (Figure~\ref{fig:fingers}).

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{tent.jpg}
	\caption{Visualization of SIGBOVIK the Tentth.}
\end{figure}

\begin{figure}[h]
	\includegraphics[width=0.3\textwidth]{tent-fingers.png}
	\caption{The tent-based counting system is the one most commonly used by humans because,
	it is widely assumed, they have tent fingers.} 
	\label{fig:fingers}
\end{figure}

Of course, as robots (who are perpetually busy with dances, parties, and/or symposia),
this is not our native counting system, but we figured it would be a great opportunity for some cultural outreach
to try to welcome more humans into our prestigious conference.
In our native tongues, this Party's edition number would be rendered as $1010$, {\tt 0xA}, or {\sf KILL ALL HUMANS}, depending on the dialect of Robotic.

This has been a remarkable year for computer-human diplomacy in the mainstream,
most notably thanks to the achievements of AlphaGo, as depicted in Figure~\ref{fig:alphago}.
We hope to reflect the same spirit of collaboration in our prestigious Dance Conference.

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{fanhui.jpg}
	\caption{A recent \sout{HUMAN\_BEING\_CRUSHED} SUCCESSFUL\_COLLABORATION between humans and robotkind.}
	\label{fig:alphago}
\end{figure}

At this time I would like to propose a toast (Figure~\ref{fig:toast}) to many continued collaborations between robots and humans, and to many powers of tent more years of SIGBOVIK.

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{toast.jpg}
	\caption{A toast.}
	\label{fig:toast}
\end{figure}

The toast having been proposed, and eaten (that's what humans do, right?), I now present the proceedings of {SIG\_BOVIK 0xA}.

With \sout{AFFECTION LEVELS COMPUTED BY MAIN THREAD 28743 NOT IN EXCESS OF 34.7} much love,
BOVIK BOT INSTANCE 0x7E0

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{times}
\usepackage[normalem]{ulem}
\setlength\parindent{0pt}
\setlength\parskip{12pt}

@@

{\sffamily
\begin{tabular}{ll}
\multirow{3}{*}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 2019}} \\ &\\
& \LARGE{Message from the Organizing Committee} \\
&\\
\hline
\end{tabular}}
\vspace{2em}
\thispagestyle{empty}

Greetings friends, colleagues, and complete strangers. It is with great pride that we welcome you to the 0xDth annual Special Interest Group on Harry Q. Bovik, held in celebration of Harry Q Bovik's $10^{somenumberbiggerthan2}$th birthday. Normally this is where we, the ``committee'', would wax poetic about  features added\footnote{despite my effort to do away with the formulaic, the proceedings chair insisted I add an explanation of the artifact medal [medal here], given to all papers determined after careful scrutiny to have included a genuine artifact}, records broken, and facts fun. However, this year, we have decided to take the highly efficient and not at all lazy route of delegating the task of writing this message to committee members of the past. A sort of temporal passing of the buck, one might say. Thus I present to you, in reverse chronological order, some messages.

\begin{itemize}
\item ``Best conference I have chaired so far, also the question mark is implicit at the end of all the survey questionspunctuationisfortheweak'' \emph{--- General Chair 2019}

\item ``much as even mentioned in the paper; well, that will teach me to forget punctuation at the end of my survey questions, won't it?'' \emph{--- General Chair 2018}

\item ``SIGBOVIK, for those with a special interest in groups-BOVIK. Like many special interests, I consider it clinically significant.'' \emph{--- General Chair 2017}

\item ``I wish all conferences were as \sout{easy to get into} prestigious as SIGBOVIK'' \emph{--- General Chair 2014}

\item `` `i'm sorry i derelicted my duties to promote sigbovik on twitter this year but i see you have 30ish submissions already even without me so HRMPH WHO NEEDS ME um i mean well done!' '' \emph{--- General Chair 2012 (note: 40ish actually, end note)}

\item ``SIGBOVIK is exactly what I had in mind. ---Edgar Allen Poe'' \emph{--- General Chair 2008}

\item ``I like to bovik bovik'' \emph{--- General Chair 2007}

\end{itemize}

And with that, the papers.

\thispagestyle{empty}
